Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-02 paper/paper.tex
captioned cdf

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{deltaCDF.png}
\caption{Fractional Change in Variance: The cumulative distribution function of the natural log of the fractional variance change when comparing our posterior to the \gaia\ catalogue. Negative numbers represent stars which have a posterior that is narrower than the \gaia\ catalogue, which is true for a large fraction of the stars. We've drawn two dashed lines. One represents the median star $(y=0.5)$ which has a fractional variation of $x=-0.3=ln(1/1.2^2)$, corresponding to an increase in precision by a factor of 1.2. Another represents the fraction of stars $(y=0.14)$ which have a fractional variance greater than $x=-1.4=ln(1/2^2)$, corresponding to an increase in precision by a factor of 2.}
\label{fig:deltaCDF}
\end{figure}
